Title here

### 2020-07-28 analysis/paper/paper.Rmd
render figuras

```{r setup, echo = FALSE,warning=FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = "",
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  cache.extra = 41,
  cache.path = "../cache/",
  collapse = TRUE,
  comment = "#>",
  dpi = 300,
  out.extra = ""
)
library(metR)
library(data.table)
library(ggplot2)
library(magrittr)
library(ggperiodic)
library(asymsam)
library(latex2exp)
library(tagger)

@@

>>>>

```{r setup, echo = FALSE,warning=FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = "",
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  cache.extra = 42,
  cache.path = "../cache/",
  collapse = TRUE,
  comment = "#>",
  dpi = 300,
  out.extra = ""
)
library(metR)
library(data.table)
library(ggplot2)
library(magrittr)
library(ggperiodic)
library(asymsam)
library(latex2exp)
library(tagger)

@@

```{r}
constants <- indices_wide %>% 
  .[, FitLm(full, asym, sym), by = .(lev)] %>% 
  rm_intercept() %>% 
  setnames("estimate", "constant")

constants %>% 
  .[term == "asym"] %>% 
  ggplot(aes(lev, constant)) +
  geom_line() +
  scale_x_level() +
  coord_flip()

asymmetry <- constants[indices, on = .NATURAL] %>% 
  .[term == "full", constant := 1] %>%
  # .[, estimate_norm := estimate_norm*constant] %>%
  dcast(lev + time ~ term, value.var = "estimate_norm") %>% 
  .[, asymmetry := atan(abs(asym)/abs(sym))/(pi/2)]

asymmetry %>% 
  .[, median(asymmetry), by = .(lev, month(time))] %>% 
  ggplot(aes(month, lev)) +
  geom_contour_fill(aes(z = V1)) +
  scale_fill_divergent(midpoint = 0.5) +
  scale_y_level()

asymmetry %>% 
  .[lev %in% main_levs] %>% 
  ggplot(aes(time, asymmetry))  +
  geom_line() +
  facet_grid(lev~.)

asymmetry %>% 
  # .[lev %in% main_levs] %>% 
  .[, FitLm(asymmetry, time, se = TRUE), by = lev] %>% 
  rm_intercept() %>% 
  # .[, term := NULL] %>% 
  .[, estimate := estimate*3600*24*365*10] %>% 
  .[, std.error := std.error*3600*24*365*10] %>% 
  # setnames("type", "term") %>% 
  ggplot(aes(lev, estimate)) +
  geom_ribbon(aes(ymax = estimate + std.error*1.96, ymin = estimate - std.error*1.96), alpha = 0.3) +
  geom_line() +
  scale_fill_brewer(palette = "Set1", aesthetics = c("color", "fill")) +
  geom_hline(yintercept = 0) +
  scale_x_level() +
  scale_y_continuous("Standard deviations per decade") +
  coord_flip() +
  tag_facets()
